\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-22 article.tex
Added content to techniques by patterns

  When we look at all techniques excluding the frequently used walking,
  sitting and L stances (Figure \ref{fig:stances_not_wsl}), we find that there
  is an even distribution of techniques except for the closed stance, the
  fixed stance and the vertical stance, which have more techniques to the
  right side (Figure \ref{fig:stances_left_not_wsl} than to the left (Figure
  \ref{fig:stances_right_not_wsl}.

@@

  There are some additional stances which needs special mentioning. The close
  stance is the only stance used by blocks, punches, strikes and thrusts. The
  parallel stance is only used for punches, whereas the vertical stance is
  only used for strikes. Only blocks are performed in the diagonal stance and
  the bending ready stance A. And finally, there are no techniques on the left
  side performed in the vertical stance.

@@

  When examining the number of different motion types to either side, we find
  that there are more motion types on the right side, than on the left. The
  right side has flying motion and consecutive motion, in additon to motion
  types found on the left side. Also, there are more flying, slow, sliding and
  consecutive motions on the right side. However, there are more fast,
  stamping, continuous and connecting motions on the left side. Comparing the
  number of motion types on both sides reveals that there are equal amounts of
  slow, jumping, dodging, double stepping and shifting motions, although with
  different groups of techniques (Figures \ref{fig:motion_left_not_n},
  \ref{fig:motion_right_not_n}.

%\SubSection{Techniques by Patterns}

  %% all techniques by patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
    %\caption{All techniques by patterns.}
    %\label{fig:patterns_all}
  %\end{figure}

  %% left techniques by patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
    %\caption{Left techniques by patterns.}
    %\label{fig:patterns_left}
  %\end{figure}

  %% right techniques by patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
    %\caption{Right techniques by patterns.}
    %\label{fig:patterns_right}
  %\end{figure}

  %% all techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    %\caption{All techniques by black belt patterns.}
    %\label{fig:patterns_black_all}
  %\end{figure}

  %% left techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
    %\caption{Left techniques by black belt patterns.}
    %\label{fig:patterns_black_left}
  %\end{figure}

  %% right techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
    %\caption{Right techniques by black belt patterns.}
    %\label{fig:patterns_black_right}
  %\end{figure}

  %% all techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    %\caption{All techniques by color belt patterns.}
    %\label{fig:patterns_color_all}
  %\end{figure}

  %% left techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
    %\caption{Left techniques by color belt patterns.}
    %\label{fig:patterns_color_left}
  %\end{figure}

  %% right techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
    %\caption{Right techniques by color belt patterns.}
    %\label{fig:patterns_color_right}
  %\end{figure}

>>>>

  When we look at all techniques excluding the frequently used walking,
  sitting and L stances (Figure \ref{fig:stances_not_wsl}), we find that there
  is an even distribution of techniques except for the closed stance, the
  fixed stance and the vertical stance, which have more techniques to the
  right side (Figure \ref{fig:stances_left_not_wsl}) than to the left (Figure
  \ref{fig:stances_right_not_wsl}).

@@

  There are some additional stances which needs special mentioning. The close
  stance is the only stance used by blocks, punches, strikes and thrusts. The
  parallel stance is only used for punches, whereas the vertical stance is
  only used for strikes. Only blocks are performed in the diagonal stance and
  the bending ready stance A. Finally, there are no techniques on the left
  side performed in the vertical stance.

@@

  When examining the number of different motion types to either side, we find
  that there are more motion types on the right side, than on the left. The
  right side has flying motion and consecutive motion, in addition to motion
  types found on the left side. Also, there are more flying, slow, sliding and
  consecutive motions on the right side. However, there are more fast,
  stamping, continuous and connecting motions on the left side. Comparing the
  number of motion types on both sides reveals that there are equal amounts of
  slow, jumping, dodging, double stepping and shifting motions, although with
  different groups of techniques (Figures \ref{fig:motion_left_not_n},
  \ref{fig:motion_right_not_n}.

\SubSection{Techniques by Patterns}

  With a few exceptions, all techniques by all patterns for both sides, follow
  the same trend, where there are most blocks, then there are more punches
  than strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).

  % all techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
    \caption{All techniques by patterns.}
    \label{fig:patterns_all}
  \end{figure}

  The exceptions for all techniques on both sides are: Chon-Ji (having more
  blocks than punches), Choong-Moo, Choong-Jang and Juche (with more punches
  than strikes) and Po-Eun (where there are more strikes than thrusts).

  % left techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
    \caption{Left techniques by patterns.}
    \label{fig:patterns_left}
  \end{figure}

  % right techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
    \caption{Right techniques by patterns.}
    \label{fig:patterns_right}
  \end{figure}

  There are, however, patterns which don't follow the exceptions described
  above (Figures \ref{fig:patterns_left}, \ref{fig:patterns_right}). There
  are, for instance, more punches than blocks in patterns Chon-Ji and Dan-Gun
  on the right side than there are on the left side. And, when we compare the
  number of punches to strikes, both Toi-Gae and Choong-Moo have an equal
  amount of punches and strikes on the left side. Lastly, there is Choong-Jang
  with more strikes than punches on the right side.

  \subsubsection{Colored Belt Patterns}

  % all techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    \caption{All techniques by color belt patterns.}
    \label{fig:patterns_color_all}
  \end{figure}

  % left techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
    %\caption{Left techniques by color belt patterns.}
    %\label{fig:patterns_color_left}
  %\end{figure}

  % right techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
    %\caption{Right techniques by color belt patterns.}
    %\label{fig:patterns_color_right}
  %\end{figure}

  \subsubsection{Black Belt Patterns}

  % all techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    \caption{All techniques by black belt patterns.}
    \label{fig:patterns_black_all}
  \end{figure}

  % left techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
    %\caption{Left techniques by black belt patterns.}
    %\label{fig:patterns_black_left}
  %\end{figure}

  % right techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
    %\caption{Right techniques by black belt patterns.}
    %\label{fig:patterns_black_right}
  %\end{figure}
